\emph{Light Exposure Behavior Assessment (LEBA)}: Develop of a novel instrument to capture light exposure-related behaviours

### 2021-09-14 manuscript.Rmd
Added affiliations

```{r IRT data, eval=FALSE, include=FALSE}

@@

@@

# Item Fit ####

## F1 Item Fit ####
F1_itemfit <- itemfit(F1_fit,fit_stats = c("S_X2", "G2","Zh", "infit"),
                                  impute=10)

F1.missfit <- F1_itemfit[F1_itemfit$p.S_X2 < 0.05, ]

## F2 Item Fit ####
F2_itemfit <- itemfit(F2_fit,fit_stats = c("S_X2", "G2","Zh", "infit"),
                      impute=10)

F2.missfit <- F2_itemfit[F2_itemfit$p.S_X2 < 0.05, ]

## F3 Item Fit ####
F3_itemfit <- itemfit(F3_fit,fit_stats = c("S_X2", "G2","Zh", "infit"),
                      impute=10)

F3.missfit <- F3_itemfit[F3_itemfit$p.S_X2 < 0.05, ]

## F4 Item Fit ####
F4_itemfit <- itemfit(F4_fit,fit_stats = c("S_X2", "G2","Zh", "infit"),
                      impute=10)

F4.missfit <- F4_itemfit[F4_itemfit$p.S_X2 < 0.05, ]

## F5 Item Fit ####
F5_itemfit <- itemfit(F5_fit,fit_stats = c("S_X2", "G2","Zh", "infit"),
                      impute=10)

F5.missfit <- F5_itemfit[F5_itemfit$p.S_X2 < 0.05, ]

# Plots ####
## F1 Plots ####
F1_OCC <- plot(F1_fit, type = "trace", facet =T, main = "Blue Filter OCC")
F1_info <- plot(F1_fit, type = "infoSE", main = "Blue Filter Test Information")
F1_iteminfo <- plot(F1_fit, type = "infotrace", main = "Blue Filter Item Information")

## F2 Plots ####
F2_OCC <- plot(F2_fit, type = "trace", facet =T, main = "Natural Light OCC")
F2_info <- plot(F2_fit, type = "infoSE", main = "Natural Light Test Information")
F2_iteminfo <- plot(F2_fit, type = "infotrace", main = "Natural Light Item Information")

## F3 Plots ####
F3_OCC <-plot(F3_fit, type = "trace", facet =T, main = "Smart Device OCC")
F3_info <- plot(F3_fit, type = "infoSE", main = "Smart Device Test Information")
F3_iteminfo <- plot(F3_fit, type = "infotrace", main = "Smart Device Item Information")

## F4 Plots ####
F4_OCC <-plot(F4_fit, type = "trace", facet =T, main = "Sleep Environment OCC")
F4_info <- plot(F4_fit, type = "infoSE", main = "Sleep Environment Test Information")
F4_iteminfo <- plot(F4_fit, type = "infotrace", main = "Sleep Environment Item Information")

## F5 Plots ####
F5_OCC <-plot(F5_fit, type = "trace", facet =T, main = "Electric Light OCC")
F5_info <- plot(F5_fit, type = "infoSE", main = "Electric Light Test Information")
F5_iteminfo <- plot(F5_fit, type = "infotrace", main = "Electric Light Item Information")

## Plot grid ####
library(cowplot)
plot_grid(F1_OCC, F2_OCC,F3_OCC,F4_OCC,F5_OCC, 
          labels = c('A', 'B','C', 'D', 'E' ), label_size = 10)

plot_grid(F1_info, F2_info,F3_info,F4_info,F5_info, 
          labels = c('A', 'B','C', 'D', 'E' ), label_size = 10)

plot_grid(F1_iteminfo, F2_iteminfo,F3_iteminfo,F4_iteminfo,F5_iteminfo, 
          labels = c('A', 'B','C', 'D', 'E' ), label_size = 10)

@@

>>>>

```{r IRT data, include=FALSE}

@@

itemparameters <- rbind(F1_items,F2_items, F3_items, F4_items,F5_items)

@@

# Plots ####
## F1 Plots ####
F1_OCC <- plot(F1_fit, type = "trace", facet =T, main = "Blue Filter OCC")
F1_info <- plot(F1_fit, type = "infoSE", main = "Blue Filter Test Information")
F1_iteminfo <- plot(F1_fit, type = "infotrace", 
                    facet_items = T, main = NULL)

## F2 Plots ####
F2_OCC <- plot(F2_fit, type = "trace", facet =T, main = "Natural Light OCC")
F2_info <- plot(F2_fit, type = "infoSE", main = "Natural Light Test Information")
F2_iteminfo <- plot(F2_fit, type = "infotrace", facet_items = T, main = NULL)

## F3 Plots ####
F3_OCC <-plot(F3_fit, type = "trace", facet =T, main = "Smart Device OCC")
F3_info <- plot(F3_fit, type = "infoSE", main = "Smart Device Test Information")
F3_iteminfo <- plot(F3_fit, type = "infotrace", 
                    facet_items = T, main = NULL)

## F4 Plots ####
F4_OCC <-plot(F4_fit, type = "trace", facet =T, main = "Sleep Environment OCC")
F4_info <- plot(F4_fit, type = "infoSE", main = "Sleep Environment Test Information")
F4_iteminfo <- plot(F4_fit, type = "infotrace", facet_items = T,main = NULL)

## F5 Plots ####
F5_OCC <-plot(F5_fit, type = "trace", facet =T, main = "Electric Light OCC")
F5_info <- plot(F5_fit, type = "infoSE", main = "Electric Light Test Information")
F5_iteminfo <- plot(F5_fit, type = "infotrace", facet_items = T,main = NULL)

## Plot grid ####
library(cowplot)
OCC <- plot_grid(F1_OCC, F2_OCC,F3_OCC,F4_OCC,F5_OCC, 
          labels = c('A', 'B','C', 'D', 'E' ), label_size = 10)

Test_Info <- plot_grid(F1_info, F2_info,F3_info,F4_info,F5_info, 
          labels = c('A', 'B','C', 'D', 'E' ), label_size = 10)

Item_Information <- plot_grid(F1_iteminfo, F2_iteminfo,F3_iteminfo,F4_iteminfo,F5_iteminfo, 
          labels = c('A', 'B','C', 'D', 'E' ), label_size = 10)

@@

We combined the EFA and CFA sample (N= 690) and fit each factor of LEBA as a unidimensional construct, and used the graded response model to obtain item parameters(\@ref(tab:IRTparameters). Item discrimination indicates the pattern of variation in the categorical responses with the changes in latent trait, and item information curve (IIC) indicates the amount of information an item carries along the latent trait continuum. Currently, apart from some general suggestions, there exists no definitive rule to judge the item discrimination and item information parameter quality. In this current study, we reported the item discrimination parameter and only discarded the items with relatively flat item information curve (information <.2). @bakerBasicsItemResponse2017 categorized the item discrimination in as none = 0; very low =0.01 to 0.34; low = 0.35 to 0.64; moderate = 0.65 to 1.34 ; high = 1.35 to 1.69; very high >1.70. Among the 23 items, 10 items were highly discriminating. Items 16 and 33 had very high discrimination parameters (28.55 & 13.50), indicating their limited applicability to people with a very high level of the latent attribute. Examination of the item information curve indicated 6 items (1, 25, 9, 38, 30, & 41) had relatively flat information curves thus discarded.

```{r IRTparameters}
apa_table(itemparameters, caption = "IRT Item parameters for the LEBA Scale", note = "a = item discrimination parameter; b(1-4) = response category difficulty parameter")
```

```{r Iteminformationcurve, fig.cap="Item information curves (A) blue filter (B) natural light (C)smart device (D)sleep environment (E)electic light", warning=FALSE, out.width="120%", out.height="150%"}
plot_grid(F1_iteminfo, F2_iteminfo,F3_iteminfo,F4_iteminfo,F5_iteminfo, 
          labels = c('A', 'B','C', 'D', 'E' ), label_size = 10 )

```{r}
F2.redu <- sem.data %>% 
  dplyr::select(item11,  item10 , item12, item7, Ritem8)
F3.redu <- sem.data %>% 
 dplyr::select(item27, item3,  item40)

F4.redu <- sem.data %>% 
 dplyr::select(item32, item35,  item33)

F5 <- sem.data %>% 
  dplyr::select(item46, item45, item25 )
```
